\bf Focusing on Fast Neural Network Inference

### 2018-05-17 wnmt.2018/wnmt.tex
cast

Our first system uses gated recurrent units (GRU) throughout, trained with Marian, but submitted both systems using the Amun inference engine.

>>>>

Our first system uses gated recurrent units (GRU) throughout, trained with Marian~\citep{junczys2018marian}, but submitted both systems using the Amun inference engine.
